Re-run, Repeat, Reproduce, Replicate, Re-use:\\Transforming Code into Scientific Contributions

### 2017-05-20 main.tex
Corrupted document

\documentclass[a4paper,11pt]{article}

% Wider margins (compared to default)
\usepackage[margin=2.5cm]{geometry}

% English support (typography and hyphenation)
\usepackage[english]{babel}

% Unicode encoding
\usepackage[utf8]{inputenc}

% Better default font (Libertine and Inconsolata)
\usepackage[ttscale=.875]{libertine}
\usepackage[scaled=0.96]{zi4}

% Biber
\usepackage[backend=biber, style=numeric, natbib=true]{biblatex}
\bibliography{library.bib}

% Graphics
\usepackage{graphicx}

% Code Listing
\usepackage{listings}
\usepackage[framemethod=tikz]{mdframed}
\makeatletter
\def\mdf@@codeheading{Code Listings}
\define@key{mdf}{title}{\def\mdf@@codeheading{#1}}
\mdfdefinestyle{lstlisting}{%
  backgroundcolor=black!2.5,
  innertopmargin=2pt,
  middlelinewidth=0.75pt,
  outerlinewidth=9pt,
  outerlinecolor=white,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  leftmargin=0pt,
  rightmargin=0pt,
  rightline=false,
  leftline=false,
  bottomline=false,
  skipabove=\topskip,
  skipbelow=\topskip,
  roundcorner=0pt,
  singleextra={
    \node[text=black, % fill=white, draw,
          anchor=south west, yshift=-0.25pt, xshift=5pt,
          font=\footnotesize] at (O|-P) {\csname mdf@@codeheading\endcsname};},
  firstextra={
    \node[text=black, % fill=white, draw,
          anchor=south west, yshift=-0.5pt, xshift=5pt,
          font=\footnotesize] at (O|-P) {\csname mdf@@codeheading\endcsname};}
}

\lstset{ %
  basicstyle=\small\tt\linespread{0.75},
  language=Python,
  commentstyle=\color{gray},
  columns=fullflexible,
}

\lstnewenvironment{code}[2][]{%
  \lstset{#1}%
  \mdframed[style=lstlisting,title={#2}]%
}{\endmdframed}

%\usepackage{listings}
%\surroundwithmdframed[
%%  hidealllines=true,
%  linewidth=0.25pt,
%  linecolor=black!50,
%  backgroundcolor=black!4,
%  innerleftmargin=8pt,
%  innertopmargin=3pt,
%  innerbottommargin=3pt]{lstlisting}
%\lstset{ %
%  basicstyle=\small\tt\linespread{0.75},
%  language=Python,
%  commentstyle=\color{gray},
%  columns=fullflexible,
%}

% Hyperref
\usepackage{xcolor}
\definecolor{blendedblue}{rgb}{0.2, 0.2, 0.6}
\definecolor{blendedred}{rgb}{0.8, 0.2, 0.2}
\usepackage[bookmarks=true,
            breaklinks=true,
            pdfborder={0 0 0},
            citecolor=blendedblue,
            colorlinks=true,
            linkcolor=blendedblue,
            urlcolor=blendedblue,
            citecolor=blendedblue,
            linktocpage=false,
            hyperindex=true,
            linkbordercolor=white]{hyperref}
\usepackage{hyperref}
\hypersetup{colorlinks=true}

\title{Re-run, Repeat, Reproduce, Replicate, Re-use:\\Transforming Code into Scientific Contributions}
% \title{Run Python, run!}
% \title{The R Quintuplet (R$^5$)}

\author{Nicolas P. Rougier and Fabien C. Y. Benureau}
\date{\today}

\begin{document}
\maketitle

% -------------------------
\section*{Introduction (R$^{\mathbf 0}$)}

@@

In our case, the R$^0$ version of our tiny walker seems to imply
that any version of Python would be fine.
This not the case because it uses the print {\em instruction} and the {\tt xrange} operator, both specific to Python 2.
The print {\em instruction}, available in Python 2 (widely used, installed by default in many operating systems), 
has been deprecated in Python 3 (first released in 2008, almost a decade ago)
in favor or a  print {\em function}.
The {\tt xrange} operator has been replaced by the {\tt range} operator in Python 3.
In order to try to future-proof the code a bit, we might as well target Python 3, as is done in the R$^1$ version.
Incidentally, it remains compatible with Python 2.

@@

As explained by Peng et al. \cite{Peng:2006}, {\em the replication of important findings by multiple independent investigators is fundamental to the accumulation of scientific evidence.}\\

>>>>

-
% -------------------------
\section*{Introduction (R$^{\mathbf 0}$)}

@@

In our case, the R$^0$ version of our tiny walker seems to imply
that any version of Python would be fine.
This not the case because it uses the print {\em instruction} and the {\tt xrange} operator, both specific to Python 2.
The print {\em instruction}, available in Python 2 (still widely used, will stop to be supported in 2020), 
has been deprecated in Python 3 (first released in 2008, almost a decade ago)
in favor or a  print {\em function}.
The {\tt xrange} operator has been replaced by the {\tt range} operator in Python 3.
In order to try to future-proof the code a bit, we might as well target Python 3, as is done in the R$^1$ version.
Incidentally, it remains compatible with Python 2.

@@

As explained by Peng et al. \cite{Peng:2006}, {\em the replication of important findings by multiple independent investigators is fundamental to the accumulation of scientific evidence}. Replicability is the assumption that any article that does not provide the code source makes: that the description it provides of the algorithms is sufficiently precise and complete to re-obtain the results it presents.
